%Raoul Rego's CV 
\documentclass[line]{resume}
\usepackage{tabularx}

\begin{document}

\name{Raoul A. Rego}
\begin{center}
	\contact {(912) 346-6060}{\href{mailto:raoulrego@gmail.com}{raoulrego@gmail.com}}{\href{https://raoul.digital}{https://raoul.digital}}
\end{center}
\vspace{-9px}
\section{Education}
\textbf{Georgia Institute of Technology} \hfill \textbf{Atlanta, GA} \\
Bachelor of Science in Computer Science  \hfill December 2018

\vspace{-3px}
\section{Experience}
\vspace{-1px}

\joblocation{Microsoft}{Redmond, WA}
\titledate{Software Engineer}{March 2022 - present}
\begin{myitemize}
	\item Worked on creating features for internal automation platform. Worked on creating features for out conversational UI chatbot as well as telemetry, automated ticket routing handling,
	and notification features for email and Microsoft Teams
	\item Wrote complex dialog workflows for our chatbot, utilzed to create over 20,000 tickets per week by thousands of users. The estimated ROI of certain workflows I created were \$100k+. Workflows I contributed to had an ROI \$1Mil+. 
	\item Begin integration of enterprise ChatGPT into our chatbot to improve the quality of our chatbot's responses when answering user questions.
	\item Collaborated with project managers to create PowerBi dashboards to indicate ROI of team's contributions as well as the health of our platform.
	\item Added robustness features to our application like rewriting our retry mechanism to use Polly, eliminating hundres or reocurring production incidents and improving reliability for users.
	\item Led learning sessions for teams on topics such as improving our unit testing, and utilizing C\# features such as Records and Nullable annotations.
	\item Architected new notificaiton feature utilized by thousands of users to inform them of required approvals for tickets.
\end{myitemize}

\vspace{2px}
\joblocation{Adobe}{Austin, TX}
\titledate{Software Engineer}{February 2019 - March 2022}
\begin{myitemize}
	\item Core developer for Magento 2 Open Source and Enterprise e-commerce applications.
	\item Increased performance of all pull request builds by rewriting internal semantic version checker to reduce memory usage by GBs and decrease PR check execution from 2 hour to 30 minutes.
	\item Created Github bot to ensure all pull requests conform to ``Definition of Done'' guidelines. This bot was used on every internal project at Magento.
	\item Developed build scripts to deploy releases of Magento for internal testing and public releases. Releases were used to serve over 250,000 active online stores.
	\item Upgraded PayPal integration process to latest  This is the most utilized payment solution on our platform and was utilized by over 100,000 stores. 
	\item Wrote PHP and JS integration/unit tests and Codeception end-to-end functional tests when creating new features and bug fixes to ensure all new changes had appropriate coverage.
	\item Achieved the Magento Certification, a demonstration of developer competency for the Magento 2 Open Source platform.
\end{myitemize}

\vspace{2px}

\joblocation{AT\&T}{El Segundo, CA}
\titledate{Entertainment Group Summer Intern}{June 2017 - August 2017}
\joblocation{Dell}{Round Rock, TX}
\titledate{Dell Financial Services IT Intern}{May 2016 - August 2016}
\vspace{2px}
\joblocation{Nead Werx}{Atlanta, GA}
\titledate{Junior Mobile Engineer}{May 2014 - December 2015}

\vspace{-2px}
\section{Skills}
\vspace{-1px}
\begin{tabularx}{\linewidth}{X}
	\textbf{Languages:} C\#, F\#, PHP, Java, Python, JavaScript, Bash, C, Objective-C, PL/SQL, \LaTeX \\
	\textbf{Frameworks \& Platforms:} .NET, React, Node.js, Android, iOS, Spring, Magento \\
	\textbf{Other Tooling \& System Administration:} Azure, Docker, Composer, Vagrant, Git, VIM \\
\end{tabularx}

\end{document}
