%Raoul Rego's Cover Letter Template

\documentclass{letter}
\usepackage[us,12hr]{datetime}
\usepackage{hyperref}
\signature{Raoul Rego \\}
\address{1726 Defoor Ave. \\ Unit B. \\ Atlanta, GA}
%\date{\mmddyyyydate\today}

\begin{document}
\begin{letter}{}
\opening{Dear Sir or Madam:}

I spoke to recruiters for Citi at the College of Computing Georgia Tech career fair and I was interested in an internship position for the summer at Citi. I'm a 3rd year CS major at the Georgia Institute of Technology specializing in Information Internetworks and System Architecture. I have 3 co-op semesters worth of experience in professional mobile application development and a solid grasp of software development fundamentals. 

I'm partial to the application development track, because I plan on doing that in the future. However, I would be interested in the Production suppport track as well; my primary goal with this internship is to expose myself to new things. Exploring this track would provide a very unique experience.

I would be a great fit for this internship position because I truly love learning about software development and because I already have experience in professional software development. Moreover, I have extensive experience in UNIX, Java, and SQL from my previous position. I also am confident in my Python skills from using them to create web applications with Django. As described to me by the recruiter, the internship gives me broad exposure to what Citi does, to working at a large company, and to working in another country; I think that experience would be invaluable.


\closing{Regards,}
\end{letter}
\end{document}

