%Raoul Rego's Cover Letter Template

\documentclass{letter}
\usepackage[us,12hr]{datetime}
\usepackage{hyperref}
\signature{Raoul Rego \\}
\address{1042 McMillan St.\\Atlanta, GA 30318}
%\date{\mmddyyyydate\today}
\begin{document}
\begin{letter}{}
	\opening{To the Hiring Manager}

	I am extremely interested in full-time opportunities at the New York Times. As a long time reader, it would be incredible to work at this organization. I have had significant experience in web development at companies varying from a small business, like Nead Werx, to a large multinational like AT\&T, so I am very adaptable to various stacks and development methodologies.

	I will be graduating from the Georgia Institute of Technology in December of this year with a Bachelor's of Computer Science. As such, I am actively pursuing full-time opportunities prior graduation. Despite being a new graduate, I have worked along the spectrum of application development. I started at Nead Werx in Atlanta, where I worked for three semesters, doing mobile development for Android and iOS and building out the new REST API in PHP. After that position, I worked at Dell, developing their backend for Dell Financial Services. I was involved in writing .NET and PL/SQL code to handle credit checking, particularly the backend for the SOAP API calls. My last internship was at AT\&T Entertainment Group where I was doing full stack development, working on the CDN manager microservice, which we used to manage CDNs to deliver video content. At AT\&T, I utilized Java and Spring Boot to build the microservice, and JavaScript and Polymer to build the front-end client. Additionally, I work at the student-run radio station, WREK, at Georgia Tech as part of the engineering staff and was previously the webmaster for the organization. At this position, I was responsible for several tasks including automating updating our TLS certificates, resolving database issues, managing the Wordpress CMS, as well as writing scripts to handle our internal email system.

	I would be most interested in working on the CMS team, as your custom CMS system, Scoop, appears very sophisticated and feature packed. However, I am much more interested in working at the New York Times than any one team in particular, so I am very open to different positions where I can leverage my skills.

\closing{Regards,}
\end{letter}
\end{document}
