%Raoul Rego's Cover Letter Template

\documentclass{letter}
\usepackage[us,12hr]{datetime}
\usepackage{hyperref}
\signature{Raoul Rego \\}
\address{1726 Defoor Ave. \\ Unit B. \\ Atlanta, GA}

\begin{document}
\begin{letter}{}
\opening{Dear Sir or Madam:}

I spoke to recruiters for Disney at the College of Computing Georgia Tech career fair and I was interested in an internship position for the summer here. I'm a 3rd year CS major at the Georgia Institute of Technology specializing in Information Internetworks and System Architecture. I have 3 co-op semesters worth of experience in professional mobile application development and a solid grasp of software development fundamentals. 

I'm partial to fullstack web development because I plan on doing that in the future. However, I would be interested in other, perhaps unrelated development positions because my primary goal with this internship is to expose myself to new things. Disney is such a huge, and iconic entertainment company that the amount of possibilies for exploration are really amazing.

I would be a great fit for this internship position because I truly love learning about software development and because I already have experience in professional software development.  As I stated before, I specifically have significant experience in mobile and middleware development. Of course, I am also interesd in the position because I also grew up with the various video casettes of Disney movies. As described to me by the recruiter, the internship gives me broad exposure to what Disney does behind the scenes and to working at a large company; I think that experience would be invaluable.


\closing{Regards,}
\end{letter}
\end{document}

