%Raoul Rego's Cover Letter Template

\documentclass{letter}
\usepackage[us,12hr]{datetime}
\usepackage{hyperref}
\signature{Raoul Rego \\}
\address{1726 Defoor Ave. \\ Unit B. \\ Atlanta, GA}

\begin{document}
\begin{letter}{}
\opening{Dear Sir or Madam:}

I spoke to recruiters for The Home Depot at the College of Computing Georgia Tech virtual career fair and I was interested in an internship position for the summer. I'm a 3rd year CS major at the Georgia Institute of Technology specializing in Information Internetworks and System Architecture. I have 3 co-op semesters worth of experience in professional mobile application development and a solid grasp of software development fundamentals. 

I'm particularly interested in a position at The Home Depot because I have not worked in large enterprise environment before. My previous position was as a Junior Mobile Developer at Nead Werx. Nead Werx provides the ERP (called xERP) solutions for The Home Depot, so I'm quite familiar and experienced with your company's processes. I worked on the Android, iOS, and middleware portions of this application.

I would be a great fit for this internship position because I truly love learning about software development and because I already have experience in professional software development. As I have said before, I have had experience working on products for the Home Depot and it would great to continue development at this company. I think that experience of working at a large company would be invaluable.

\closing{Regards,}
\end{letter}
\end{document}

