%Raoul Rego's Cover Letter Template

\documentclass{letter}
\usepackage[us,12hr]{datetime}
\usepackage{hyperref}
\signature{Raoul Rego\\}

\begin{document}
\begin{letter}{}
\opening{Dear Sir or Madam:}

I spoke to recruiters for Turner Broadcasting at the College of Computing Georgia Tech career fair and I was interested in an internship position for the spring here. I am a 3rd year CS major at the Georgia Institute of Technology specializing in Information Internetworks and System Architecture. I have experience in professional software development, particularly with respect to web and mobile development, and a solid grasp of software development fundamentals. 

I'm partial to fullstack web development because I plan on doing that in the future. However, I would be interested in other, perhaps unrelated development positions because my primary goal with this internship is to expose myself to new things. Turner is such a huge and iconic media company that the amount of possibilities for exploration is really amazing.

I would be a great fit for this internship position because I truly love learning about software development and because I already have experience in professional software development.  As I stated before, I specifically have significant experience in mobile and middleware development in a professional environment. I have also worked on various PHP sites for personal projects. Of course, I am also interested in the position because the significant time I have spent in watching CNN and Cartoon Network. As described to me by the recruiter, the internship gives me broad exposure to what Turner does behind the scenes and to working at a large company; I think that this experience would be invaluable.


\closing{Regards,}
\end{letter}
\end{document}

