%Raoul Rego's CV 
\documentclass[line]{resume}
\usepackage{tabularx}

\begin{document}

\name{Raoul A. Rego}
\begin{center}
	\contact {(912) 346-6060}{\href{mailto:raoulrego@gmail.com}{raoulrego@gmail.com}}{\href{https://raoul.digital}{https://raoul.digital}}
\end{center}
\vspace{-1mm}
\section{Education}
\textbf{Georgia Institute of Technology} \hfill \textbf{Atlanta, GA} \\
Bachelor of Science in Computer Science  \hfill December 2018

\vspace{-3px}
\section{Experience}
\vspace{-1px}

\joblocation{Adobe}{Austin, TX}
\titledate{Software Engineer}{February 2019 - present} 
\begin{myitemize}
	\item Core developer for Magento 2 Open Source and Enterprise e-commerce applications.
	\item Increased performance of pull request builds by rewriting internal semantic version checker to reduce memory usage by GBs and decrease execution time by over an hour.
	\item Created Github bot to ensure all pull requests conform to ``Definition of Done'' guidelines. This bot is used on every internal project at Magento.
	\item Fixed, configured, and ran builds to deploy releases of Magento for internal testing and public releases. These public releases are run by over 250,000 active online stores.
	\item Improved code quality of core and infrastructure codebases by performing numerous code reviews on contributions from individual contributors, external vendors, other internal teams, and my own team.
	\item Identified breaking and incompatible changes (BIC) for patch and minor releases and coordinated approval process for these BIC. Our team reduced this multiweek approval process to a few hours by fixing the approval process for delivering code so that approvals are completed and documented prior delivery.
	\item Wrote PHP and JS integration/unit tests and Codeception end-to-end functional tests when creating new features and bug fixes to ensure all new changes had appropriate coverage.
	\item Upgraded PayPal integration to latest SDK. This is the most utilized payment solution on our platform and will be used by thousands of stores.
	\item Achieved the Magento Associate Certification, a demonstration of developer competency for the Magento 2 Open Source platform.
\end{myitemize}
\vspace{2px}
\joblocation{AT\&T}{El Segundo, CA}
\titledatedescrip{Entertainment Group Summer Intern}{June 2017 - August 2017}{Java Spring and JavaScript Polymer development}
\vspace{2px}
\joblocation{Dell}{Round Rock, TX}
\titledatedescrip{Dell Financial Services IT Intern}{May 2016 - August 2016}{C\# .NET development}

\vspace{2px}

\joblocation{Nead Werx}{Atlanta, GA}
\titledatedescrip{Junior Mobile Engineer}{May 2014 - December 2015}{Android Java, Objective-C iOS, and PHP middleware development}

\vspace{-2px}
\section{Skills}
\vspace{-1px}
\begin{tabularx}{\linewidth}{X}
	\textbf{Languages:} PHP, Java, Python, JavaScript, Bash, C, Objective-C, PL/SQL, Verilog, \LaTeX \\
	\textbf{Frameworks \& Platforms:} Magento, jQuery, Polymer, React, Node.js, Android, iOS, Spring, .NET \\
	\textbf{Tooling \& System Administration:} Docker, Composer, Vagrant, Git, VIM \\
\end{tabularx}

\end{document}
